---
title: "Fantasy MLS Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
  
---

```{r setup, include=FALSE}
set.local <- "C:/Users/Lee/OneDrive/FMLS folder/"
library(flexdashboard)
require("ggplot2")
require("dplyr")
require("tidyr")
require("ggthemes")
require("knitr")
require(DT)
Starter <- read.csv(paste(set.local,"DataPredicted.csv",sep = ""), stringsAsFactors = FALSE) %>% select(-X)
Data <- Starter[,1:32]
Predictions <- Starter %>% select(ID,Game,starts_with("L"),-Location)

if(nrow(Data %>% filter(Season == "Current")) == 0){Data[Data$Season == "16/17 Season","Season"] <- "Current"}
Data$Points <- Starter$Points
Data$pred.score <- rowMeans(Predictions %>% select(contains("score")), na.rm = TRUE )
Data$pred.assist <- rowMeans(Predictions %>% select(contains("assist")), na.rm = TRUE  )
Data$pred.clean <- rowMeans(Predictions %>% select(contains("clean")), na.rm = TRUE  )
Data$pred.Save.3 <- rowMeans(Predictions %>% select(contains("S3")), na.rm = TRUE  )
Data <- Data %>% group_by(ID) %>% mutate(Pred.points = ifelse(Position == "G",
                                             sum(2,pred.score * 6,pred.assist * 3,pred.clean * 5,pred.Save.3 * 1, na.rm = TRUE),
                                      ifelse(Position == "D",
                                             sum(2,pred.score * 6,pred.assist * 3,pred.clean * 5, na.rm = TRUE),
                                      ifelse(Position == "M",
                                             sum(2,pred.score * 5,pred.assist * 3,pred.clean * 1, na.rm = TRUE),
                                      ifelse(Position == "F",
                                             sum(2,pred.score * 5,pred.assist * 3, na.rm = TRUE),NA
                                             ))))) %>% ungroup()

Top_Keepers <- Data %>% filter(Position == "G", Season == "Current") %>% group_by(Position,Name) %>%  summarise_if(is.numeric,sum) %>% arrange(Points) %>% top_n(2,Points)
Top_Defenders <- Data %>% filter(Position == "D", Season == "Current") %>% group_by(Position,Name) %>%  summarise_if(is.numeric,sum) %>% arrange(Points) %>% top_n(5,Points)
Top_Midfielders <- Data %>% filter(Position == "M", Season == "Current") %>% group_by(Position,Name) %>%  summarise_if(is.numeric,sum) %>% arrange(Points) %>% top_n(5,Points)
Top_Strikers <- Data %>% filter(Position == "F", Season == "Current") %>% group_by(Position,Name) %>%  summarise_if(is.numeric,sum) %>% arrange(Points) %>% top_n(3,Points)

Top <- rbind(Top_Keepers,Top_Defenders,Top_Midfielders,Top_Strikers)

Pred_Keepers <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "G", Season == "Current") %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(2,Pred.points)
Pred_Defenders <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "D", Season == "Current")  %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(5,Pred.points)
Pred_Midfielders <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "M", Season == "Current")  %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(5,Pred.points)
Pred_Strikers <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "F", Season == "Current")  %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(3,Pred.points)

Pred <- rbind(Pred_Keepers,Pred_Defenders,Pred_Midfielders,Pred_Strikers)

#remove later
Data <- Data %>% group_by(Season,Name) %>% arrange(Game) %>% mutate(cum.Points = cumsum(Points), cum.Minutes = cumsum(Minutes)) %>% ungroup() %>% group_by(ID) %>% mutate(PP90 = round(ifelse(cum.Minutes > 90,cum.Points / cum.Minutes * 90,0),0))

PP90_Keepers <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "G", Season == "Current") %>%  ungroup() %>% mutate(PP90 = round(PP90,2)) %>% arrange(PP90) %>%  top_n(2,PP90) %>%  top_n(2,cum.Points)
PP90_Defenders <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "D", Season == "Current")  %>%  ungroup() %>% mutate(PP90 = round(PP90,2)) %>% arrange(PP90) %>%  top_n(5,PP90) %>%  top_n(5,cum.Points)
PP90_Midfielders <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "M", Season == "Current")  %>%  ungroup() %>% mutate(PP90 = round(PP90,2)) %>% arrange(PP90) %>%  top_n(5,PP90) %>%  top_n(5,cum.Points)
PP90_Strikers <- Data %>% group_by(Name) %>% arrange(GameWeek) %>% summarise_all(funs(last)) %>% filter(Position == "F", Season == "Current")  %>%  ungroup() %>% mutate(PP90 = round(PP90,2)) %>% arrange(PP90) %>%  top_n(3,PP90) %>%  top_n(3,cum.Points)

PP90 <- rbind(PP90_Keepers,PP90_Defenders,PP90_Midfielders,PP90_Strikers)

Team <- Data %>% filter(Season == "Current") %>% ungroup() %>% group_by(Team) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3, -GameWeek, -SeasonGame) %>% summarise_if(is.numeric,funs(Average = mean,Total = sum))%>% mutate_if(is.numeric,round, digits = 2)

Player <- Data %>% filter(Season == "Current") %>% ungroup() %>% group_by(Name) %>% select(-ID,-Number ,-Game, -Against, -Location, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3, -Pred.points) %>% summarise_if(is.numeric,funs(Average = mean,Total = sum)) %>% mutate_if(is.numeric,round, digits = 2)

Player.Probabilities <- Data %>% filter(Season == "Current") %>% group_by(Name) %>% arrange(Game) %>% summarise_all(funs(last)) %>% select(Name,Team, Position, pred.score, pred.clean, pred.assist, pred.Save.3, Pred.points)%>% mutate_if(is.numeric,round, digits = 2)
```

Best Team
==========================================


Row {.tabset}
------------------------------------------

Here are several different methods of selecting your team as well as a comparison of each method.

### Predicted Best (Engine1)

```{r}
Pred %>% ggplot(aes(Name,Pred.points,fill = Position)) + geom_bar(stat = "identity") + theme_tufte() + scale_fill_tableau()+ coord_flip()
```

### Top Points

```{r}
Top %>% ggplot(aes(Name, Points, fill = Position)) + geom_bar(stat = "identity") + theme_tufte() + scale_fill_tableau()+ coord_flip()
```

### Highest PP90

```{r}
PP90 %>% ggplot(aes(Name, PP90, fill = Position)) + geom_bar(stat = "identity") + theme_tufte() + scale_fill_tableau()+ coord_flip()
```

### Comparison


```{r}
Compare.D <- Data %>% select(ID,Name,Position,Season, GameWeek,Game,Points,Pred.points,PP90,cum.Points) %>% group_by(Name) %>% arrange(Game) %>% mutate(lag.PP90 = lag(PP90),Point.Total = lag(cum.Points)) %>% filter(Season == "Current")
Graph <- data.frame(0,0,0,0,0)
names(Graph) <- c("GameWeek","Predicted","PP90","Total Points","Best")
for(i in 1:max(Compare.D$GameWeek)){
#predicted team
P_Keepers <- Compare.D %>% filter(Position == "G", GameWeek == i) %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(2,Pred.points) %>% top_n(2,Point.Total)
P_Defenders <- Compare.D %>% filter(Position == "D", GameWeek == i) %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(5,Pred.points) %>% top_n(5,Point.Total)
P_Midfielders <- Compare.D %>% filter(Position == "M", GameWeek == i) %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(5,Pred.points) %>% top_n(5,Point.Total)
P_Strikers <- Compare.D %>% filter(Position == "F", GameWeek == i) %>%  ungroup() %>% mutate(Pred.points = round(Pred.points,2)) %>% arrange(Pred.points) %>%  top_n(5,Pred.points) %>% top_n(3,Point.Total)
P <- rbind(P_Keepers,P_Defenders,P_Midfielders,P_Strikers) %>% top_n(11,Pred.points) %>% top_n(11,Point.Total)
Predicted <- sum(P$Points)
#PP90 team
P90_Keepers <- Compare.D %>% filter(Position == "G", GameWeek == i) %>%  ungroup() %>% mutate(lag.PP90 = round(lag.PP90,2)) %>% arrange(lag.PP90) %>%  top_n(2,lag.PP90) %>% top_n(2,Point.Total)
P90_Defenders <- Compare.D %>% filter(Position == "D", GameWeek == i) %>%  ungroup() %>% mutate(lag.PP90 = round(lag.PP90,2)) %>% arrange(lag.PP90) %>%  top_n(5,lag.PP90) %>% top_n(5,Point.Total)
P90_Midfielders <- Compare.D %>% filter(Position == "M", GameWeek == i) %>%  ungroup() %>% mutate(lag.PP90 = round(lag.PP90,2)) %>% arrange(lag.PP90) %>%  top_n(5,lag.PP90) %>% top_n(5,Point.Total)
P90_Strikers <- Compare.D %>% filter(Position == "F", GameWeek == i) %>%  ungroup() %>% mutate(lag.PP90 = round(lag.PP90,2)) %>% arrange(lag.PP90) %>%  top_n(5,lag.PP90) %>% top_n(3,Point.Total)
P90 <- rbind(P90_Keepers,P90_Defenders,P90_Midfielders,P90_Strikers) %>% top_n(11,lag.PP90) %>% top_n(11,Point.Total)
t.PP90 <- sum(P90$Points)
#Total Points
P_Keepers <- Compare.D %>% filter(Position == "G", GameWeek == i) %>%  ungroup() %>% mutate(Point.Total = round(Point.Total,2)) %>% arrange(Point.Total) %>%  top_n(2,Point.Total) %>% top_n(2,lag.PP90)
P_Defenders <- Compare.D %>% filter(Position == "D", GameWeek == i) %>%  ungroup() %>% mutate(Point.Total = round(Point.Total,2)) %>% arrange(Point.Total) %>%  top_n(5,Point.Total) %>% top_n(5,lag.PP90)
P_Midfielders <- Compare.D %>% filter(Position == "M", GameWeek == i) %>%  ungroup() %>% mutate(Point.Total = round(Point.Total,2)) %>% arrange(Point.Total) %>%  top_n(5,Point.Total) %>% top_n(5,lag.PP90)
P_Strikers <- Compare.D %>% filter(Position == "F", GameWeek == i) %>%  ungroup() %>% mutate(Point.Total = round(Point.Total,2)) %>% arrange(Point.Total) %>%  top_n(5,Point.Total) %>% top_n(3,lag.PP90)
tots <- rbind(P_Keepers,P_Defenders,P_Midfielders,P_Strikers) %>% top_n(11,Point.Total) %>% top_n(11,lag.PP90)
Total <- sum(tots$Points)
#Best
P_Keepers <- Compare.D %>% filter(Position == "G", GameWeek == i) %>%  ungroup() %>% mutate(Points = round(Points,2)) %>% arrange(Points) %>%  top_n(2,Points) %>% top_n(2,lag.PP90)
P_Defenders <- Compare.D %>% filter(Position == "D", GameWeek == i) %>%  ungroup() %>% mutate(Points = round(Points,2)) %>% arrange(Points) %>%  top_n(5,Points) %>% top_n(5,lag.PP90)
P_Midfielders <- Compare.D %>% filter(Position == "M", GameWeek == i) %>%  ungroup() %>% mutate(Points = round(Points,2)) %>% arrange(Points) %>%  top_n(5,Points) %>% top_n(5,lag.PP90)
P_Strikers <- Compare.D %>% filter(Position == "F", GameWeek == i) %>%  ungroup() %>% mutate(Points = round(Points,2)) %>% arrange(Points) %>%  top_n(5,Points) %>% top_n(3,lag.PP90)
best <- rbind(P_Keepers,P_Defenders,P_Midfielders,P_Strikers) %>% top_n(11,Points) %>% top_n(11,lag.PP90)
Best <- sum(best$Points)
Graph[i,] <- c(i,Predicted,t.PP90,Total,Best)
}
Graph2 <- Graph %>% select(-GameWeek) %>% mutate_all(cumsum)
Graph2$GameWeek <- Graph$GameWeek
Graph <- Graph2 %>% gather("Model","Value",1:4)
if(nrow(Graph2) > 4){Graph %>% ggplot(aes(GameWeek,Value,color = Model)) + geom_line() + labs(x = "Week",y = "Cumulative Points") + scale_x_continuous(breaks = seq(1,34,by = 1), expand = c(0,0)) + theme_economist_white() + scale_color_tableau()}else{Graph %>% ggplot(aes(GameWeek,Value,fill = Model)) + geom_bar(stat = "identity", position = "dodge") + labs(x = "Week",y = "Cumulative Points") + scale_x_continuous(breaks = seq(1,34,by = 1), expand = c(0,0)) + theme_economist_white() + scale_fill_tableau()}
```

Teams
==========================================

Row {.tabset .tabset-fade}
------------------------------------------

### Head to Head Goals/Goals_Allowed

```{r}
Data %>% filter(Season == "Current") %>% group_by(Team,Against) %>% summarise(Goals = sum(Goals)) %>% ggplot(aes(Team, Against)) + geom_tile(aes(fill = Goals),width = 0.9, height = 0.9) + geom_text(aes(label = Goals), colour = "White") + theme_tufte(base_size = 9)  + labs(x = "Goals Scored", y = "Goals Allowed")  + scale_y_discrete(expand = c(0, 0)) +  scale_fill_gradient(low = "Blue",high = "Orange") + theme(legend.position="none",axis.text.x = element_text(angle = 90, hjust = 1)) 
```


### Team {.no-mobile}

```{r}
datatable(Team)
```

### Player Stats {.no-mobile}

```{r}
datatable(Player)
```

### Player Probabilities {.no-mobile}

```{r}
datatable(Player.Probabilities)
```


Season 16/17
==========================================

Row {.tabset .tabset-fade}
------------------------------------------

### Head to Head Goals/Goals_Allowed 

```{r}
Data %>% filter(Season == "16/17 Season") %>% group_by(Team,Against) %>% summarise(Goals = sum(Goals)) %>% ggplot(aes(Team, Against)) + geom_tile(aes(fill = Goals),width = 0.9, height = 0.9) + geom_text(aes(label = Goals), colour = "White") + theme_tufte(base_size = 9)  + labs(x = "Goals Scored", y = "Goals Allowed")  + scale_y_discrete(expand = c(0, 0)) +  scale_fill_gradient(low = "Black",high = "Red") + theme(legend.position="none",axis.text.x = element_text(angle = 90, hjust = 1)) 
```

### Top Keepers

```{r}
Top_Keepers.1617 <- Data %>% filter(Position == "G", Season == "16/17 Season") %>% group_by(Name) %>% select(Saves,Clean.sheet) %>% summarise_all(sum) %>% arrange(Clean.sheet, Saves) %>% top_n(2,Saves) %>% select(Name)
Top_Defenders.1617 <- Data %>% filter(Position == "D", Season == "16/17 Season") %>% group_by(Name) %>% select(Goals,Assists,Clean.sheet) %>% summarise_all(sum) %>% arrange(Goals, Clean.sheet, Assists) %>% top_n(5,Clean.sheet) %>% select(Name)
Top_Midfielders.1617 <- Data %>% filter(Position == "M", Season == "16/17 Season") %>% group_by(Name) %>% select(Goals,Assists,Clean.sheet) %>% summarise_all(sum) %>% arrange(Goals,Assists, Clean.sheet) %>% top_n(5,Goals) %>% select(Name)
Top_Strikers.1617 <- Data %>% filter(Position == "F", Season == "16/17 Season") %>% group_by(Name) %>% select(Goals,Assists) %>% summarise_all(sum) %>% arrange(Goals,Assists) %>% top_n(5, Goals) %>% select(Name)

Data %>% filter(Name %in% Top_Keepers.1617$Name, Season == "16/17 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Saves = cumsum(Saves)) %>% ggplot(aes(SeasonGame, C.Saves, color = Name)) + geom_line()

```

###Top Defenders

```{r}
Data %>% filter(Name %in% Top_Defenders.1617$Name, Season == "16/17 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Cleans = cumsum(Clean.sheet)) %>% ggplot(aes(SeasonGame, C.Cleans, color = Name)) + geom_line()
```

###Top Midfielders

```{r}
Data %>% filter(Name %in% Top_Midfielders.1617$Name, Season == "16/17 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Goals = cumsum(Goals)) %>% ggplot(aes(SeasonGame, C.Goals, color = Name)) + geom_line()
```

###Top Strikers

```{r}
Data %>% filter(Name %in% Top_Strikers.1617$Name, Season == "16/17 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Goals = cumsum(Goals)) %>% ggplot(aes(SeasonGame, C.Goals, color = Name)) + geom_line()
```

### Team {.no-mobile}

```{r}
Data %>% filter(Season == "16/17 Season") %>% ungroup() %>% group_by(Team) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3) %>% summarise_all(funs(average = mean)) %>% datatable()
```

### Player Stats {.no-mobile}

```{r}
Data %>% filter(Season == "16/17 Season") %>% group_by(Name) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3) %>% summarise_all(funs(average = mean)) %>% datatable()
```

Season 15/16
==========================================

Row {.tabset .tabset-fade}
------------------------------------------


### Head to Head Goals/Goals_Allowed {data-width=1000} 

```{r}
Data %>% filter(Season == "15/16 Season") %>% group_by(Team,Against) %>% summarise(Goals = sum(Goals)) %>% ggplot(aes(Team, Against)) + geom_tile(aes(fill = Goals),width = 0.9, height = 0.9) + geom_text(aes(label = Goals), colour = "White") + theme_tufte(base_size = 9)  + labs(x = "Goals Scored", y = "Goals Allowed")  + scale_y_discrete(expand = c(0, 0)) + scale_x_discrete(expand = c(0, 0)) +  scale_fill_gradient(low = "Black",high = "Red") + theme(legend.position="none",axis.text.x = element_text(angle = 90, hjust = 1))
```

### Top Keepers

```{r}
Top_Keepers.1516 <- Data %>% filter(Position == "G", Season == "15/16 Season") %>% group_by(Name) %>% select(Saves,Clean.sheet) %>% summarise_all(sum) %>% arrange(Clean.sheet, Saves) %>% top_n(2,Saves) %>% select(Name)
Top_Defenders.1516 <- Data %>% filter(Position == "D", Season == "15/16 Season") %>% group_by(Name) %>% select(Goals,Assists,Clean.sheet) %>% summarise_all(sum) %>% arrange(Goals, Clean.sheet, Assists) %>% top_n(5,Clean.sheet) %>% select(Name)
Top_Midfielders.1516 <- Data %>% filter(Position == "M", Season == "15/16 Season") %>% group_by(Name) %>% select(Goals,Assists,Clean.sheet) %>% summarise_all(sum) %>% arrange(Goals,Assists, Clean.sheet) %>% top_n(5,Goals) %>% select(Name)
Top_Strikers.1516 <- Data %>% filter(Position == "F", Season == "15/16 Season") %>% group_by(Name) %>% select(Goals,Assists) %>% summarise_all(sum) %>% arrange(Goals,Assists) %>% top_n(5, Goals) %>% select(Name)

Data %>% filter(Name %in% Top_Keepers.1516$Name, Season == "15/16 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Saves = cumsum(Saves)) %>% ggplot(aes(SeasonGame, C.Saves, color = Name)) + geom_line()

```

###Top Defenders

```{r}
Data %>% filter(Name %in% Top_Defenders.1516$Name, Season == "15/16 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Cleans = cumsum(Clean.sheet)) %>% ggplot(aes(SeasonGame, C.Cleans, color = Name)) + geom_line()
```

###Top Midfielders

```{r}
Data %>% filter(Name %in% Top_Midfielders.1516$Name, Season == "15/16 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Goals = cumsum(Goals)) %>% ggplot(aes(SeasonGame, C.Goals, color = Name)) + geom_line()
```

###Top Strikers

```{r}
Data %>% filter(Name %in% Top_Strikers.1516$Name, Season == "15/16 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Goals = cumsum(Goals)) %>% ggplot(aes(SeasonGame, C.Goals, color = Name)) + geom_line()
```


### Team {.no-mobile}

```{r}
Data %>% filter(Season == "15/16 Season") %>% ungroup() %>% group_by(Team) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3) %>% summarise_all(funs(average = mean)) %>% datatable()
```

### Player Stats {.no-mobile}

```{r}
Data %>% filter(Season == "15/16 Season") %>% group_by(Name) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3) %>% summarise_all(funs(average = mean)) %>% datatable()
```


Season 14/15
==========================================

Row {.tabset .tabset-fade}
------------------------------------------

### Head to Head Goals/Goals_Allowed

```{r}
Data %>% filter(Season == "14/15 Season") %>% group_by(Team,Against) %>% summarise(Goals = sum(Goals)) %>% ggplot(aes(Team, Against)) + geom_tile(aes(fill = Goals),width = 0.9, height = 0.9) + geom_text(aes(label = Goals), colour = "White") + theme_tufte(base_size = 9)  + labs(x = "Goals Scored", y = "Goals Allowed")  + scale_y_discrete(expand = c(0, 0)) +  scale_fill_gradient(low = "Blue",high = "Red") + theme(legend.position="none",axis.text.x = element_text(angle = 90, hjust = 1)) 
```

### Top Keepers

```{r}
Top_Keepers.1415 <- Data %>% filter(Position == "G", Season == "14/15 Season") %>% group_by(Name) %>% select(Saves,Clean.sheet) %>% summarise_all(sum) %>% arrange(Clean.sheet, Saves) %>% top_n(2,Saves) %>% select(Name)
Top_Defenders.1415 <- Data %>% filter(Position == "D", Season == "14/15 Season") %>% group_by(Name) %>% select(Goals,Assists,Clean.sheet) %>% summarise_all(sum) %>% arrange(Goals, Clean.sheet, Assists) %>% top_n(5,Clean.sheet) %>% select(Name)
Top_Midfielders.1415 <- Data %>% filter(Position == "M", Season == "14/15 Season") %>% group_by(Name) %>% select(Goals,Assists,Clean.sheet) %>% summarise_all(sum) %>% arrange(Goals,Assists, Clean.sheet) %>% top_n(5,Goals) %>% select(Name)
Top_Strikers.1415 <- Data %>% filter(Position == "F", Season == "14/15 Season") %>% group_by(Name) %>% select(Goals,Assists) %>% summarise_all(sum) %>% arrange(Goals,Assists) %>% top_n(5, Goals) %>% select(Name)

Data %>% filter(Name %in% Top_Keepers.1415$Name, Season == "14/15 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Saves = cumsum(Saves)) %>% ggplot(aes(SeasonGame, C.Saves, color = Name)) + geom_line()

```

###Top Defenders

```{r}
Data %>% filter(Name %in% Top_Defenders.1415$Name, Season == "14/15 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Cleans = cumsum(Clean.sheet)) %>% ggplot(aes(SeasonGame, C.Cleans, color = Name)) + geom_line()
```

###Top Midfielders

```{r}
Data %>% filter(Name %in% Top_Midfielders.1415$Name, Season == "14/15 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Goals = cumsum(Goals)) %>% ggplot(aes(SeasonGame, C.Goals, color = Name)) + geom_line()
```

###Top Strikers

```{r}
Data %>% filter(Name %in% Top_Strikers.1415$Name, Season == "14/15 Season") %>% ungroup() %>% group_by(Name) %>% mutate(C.Goals = cumsum(Goals)) %>% ggplot(aes(SeasonGame, C.Goals, color = Name)) + geom_line()
```

### Team {.no-mobile}

```{r}
Data %>% filter(Season == "14/15 Season") %>% ungroup() %>% group_by(Team) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3) %>% summarise_all(funs(average = mean)) %>% datatable()
```

### Player Stats {.no-mobile}

```{r}
Data %>% filter(Season == "14/15 Season") %>% group_by(Name) %>% select(-ID, -Name, -Game, -Minutes, -Against, -Location, - Number, -Position, -scored, -brace, -hattrick, -Save.3, -Save.6, -pred.score, -pred.clean, -pred.assist, -pred.Save.3) %>% summarise_all(funs(average = mean)) %>% datatable()
```

Additional Materials, Ongoing Analysis, and the like
=====================================================

> Here I will be posting the results of various investigations that I make into the data, when I have time. Presently, the algorithms are only considering the last gameweek and cumulative statistics to determine probabilities. This will change over the coming days. Additionally, I have not yet even begun to develop solid KPIs to be used as variables in analysis so I expect model accuracy to improve modestly as time goes on. At the moment, all models predict just slightly (0.1-1%) better than the naive rule with models considering more history performing minutely better.

```{r}
#timer <- read.csv(paste(set.local,"timer.csv", sep = ""))
```

About the Author
=====================================================

Lee W Mathews is an Alexandria and Baton Rouge native of Louisiana. While in Alexandria he attended Our Lady of Prompt Succor school and Holy Savior Menard High School. He then moved down to Baton Rouge and earned two degrees from Louisiana State University. His undergraduate degree is in Biology; his favorite subjects the studies Physiology and Immunology. Lee changed directions for graduate school and attained a Master's in Analytics. He now works as an Analytical Consultant at Cognizant.

> The information provided here is my own. I make no claim to its efficacy, accuracy, objectivity, or root in reality. Whatever you do with these pages is on you; I stake none of my professional ability on this site. It is a hobby, and that alone.

> Viva Christo Rey!
